\documentclass{article}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}

\geometry{top=1in, bottom=1in, left=1in, right=1in}
\setlength\parindent{0pt}
\setlength{\parskip}{5pt}

\titleformat{\section}
  {\normalfont\normalsize\bfseries}
  {}{0em}{}
\titlespacing*{\section}{0pt}{16pt}{4pt}

\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=1.4em}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\small\thepage}
\fancyfoot[R]{\small Layer 2: Operating Model --- DRAFT}

% ── Helper: BG label ─────────────────────────────────────────────────────────
\newcommand{\bglabel}[2]{%
  \vspace{8pt}%
  \noindent{\normalsize\bfseries #1\enspace|\enspace#2}%
  \vspace{3pt}%
}

% ── Helper: gate condition ────────────────────────────────────────────────────
\newcommand{\gatecondition}[2]{%
  \vspace{6pt}%
  \noindent\textbf{Gate #1 Condition:}\enspace #2%
  \vspace{4pt}%
}

% ── Helper: AO row ────────────────────────────────────────────────────────────
\newcommand{\annualobjective}[3]{%
  \vspace{4pt}%
  \noindent\textbf{#1}\enspace #2\hfill{\small Target: #3}%
}

% ── Helper: initiative row ────────────────────────────────────────────────────
\newcommand{\initiative}[4]{%
  \begin{itemize}[leftmargin=2em, topsep=1pt]
    \item \textbf{#1}\enspace #2\hfill{\small #4}\\
          {\small Done when: #3}
  \end{itemize}%
}

% ─────────────────────────────────────────────────────────────────────────────
\begin{document}

{\large\textbf{Layer 2: Operating Model}} \hfill Jonathan Erdmann \\
{\normalsize Strategic Career Development Plan} \hfill Draft --- May 2026

\vspace{5pt}

% ════════════════════════════════════════════════════════════════════════════
\section{Phase 1 \quad Formal Credentials \& Network Establishment \hfill \normalfont\small 2026 -- 2027}
% ════════════════════════════════════════════════════════════════════════════

\bglabel{BG-01}{Complete the SMU Executive MBA with Distinction}

\annualobjective{AO-01}{Complete Term 3 maintaining GPA on track for distinction.}{2026}

\initiative{IN-01}{STRA-6231 Strategic Management for Executives}
  {Course completed; grade consistent with distinction trajectory.}{Summer 2026}

\initiative{IN-02}{BA-6230 Managing Operations for Executives}
  {Course completed; grade consistent with distinction trajectory.}{Summer 2026}

\initiative{IN-03}{BA-6210 Global Business Project}
  {Project delivered; grade consistent with distinction trajectory.}{Summer 2026}

\annualobjective{AO-02}{Complete Term 4 maintaining GPA on track for distinction.}{H2 2026}

\initiative{IN-01 -- IN-04}{Term 4 electives (4 courses, selections pending advisor confirmation)}
  {All four courses completed; grades consistent with distinction trajectory.}{H2 2026}

\annualobjective{AO-03}{Complete Term 5 and graduate with distinction.}{H1 2027}

\initiative{IN-01 -- IN-04}{Term 5 electives (4 courses, selections pending enrollment)}
  {All four courses completed; EMBA degree conferred with distinction.}{H1 2027}

\vspace{6pt}

\bglabel{BG-02}{Establish a Credible Professional Narrative and Targeted Network}

\annualobjective{AO-01}{Complete LinkedIn profile and resume rewrite for corporate strategy positioning.}{2026}

\initiative{IN-01}{LinkedIn profile rewrite}
  {Profile reflects strategy-oriented positioning; headline, summary, and experience rewritten.}{Summer 2026}

\initiative{IN-02}{Resume rewrite}
  {Resume reflects director-targeted positioning; two-page format; accomplishment language in place.}{Summer 2026}

\annualobjective{AO-02}{Build a targeted network in corporate strategy at large A\&D primes.}{2027}

\initiative{IN-01}{External network development}
  {Minimum five substantive relationships initiated with strategy professionals at target organizations.}{2026 -- 2027}

\initiative{IN-02}{LinkedIn content and professional visibility}
  {Consistent content cadence established; profile activity visible to target audience.}{2026 -- 2027}

\annualobjective{AO-03}{Establish internal visibility at Collins and identify an executive sponsor.}{2027}

\initiative{IN-01}{Build executive visibility within Collins}
  {At least two senior leaders above current management chain contacts aware of work and trajectory.}{2026 -- 2027}

\initiative{IN-02}{Secure executive sponsorship}
  {One senior leader has agreed to provide periodic guidance and advocacy; quarterly touchpoint cadence established.}{2026 -- 2027}

\newpage

\bglabel{BG-03}{Transition into a Strategy-Adjacent Role at Collins} 

\annualobjective{AO-01}{Expand current role scope to include strategy-adjacent activities.}{2026 -- 2027}

\initiative{IN-01}{Sustain and document workforce utilization performance}
  {Billable utilization at or above target for all three teams through end of 2026; performance narrative with revenue impact framing prepared.}{2026}

\initiative{IN-02}{Pursue strategy-adjacent activities within current role}
  {At least one initiative with visibility above current management chain completed; participation in BD, capture, or strategic planning activity documented.}{2026 -- 2027}

\initiative{IN-03}{Position for and pursue a strategy-adjacent role or scope expansion}
  {Active pursuit of at least one strategy-adjacent role or formal scope expansion within Collins initiated.}{H2 2026 -- 2027}

\gatecondition{1}{EMBA complete; professional narrative and digital presence established;
internal visibility initiated; executive sponsor identified.}

\newpage

% ════════════════════════════════════════════════════════════════════════════
\section{Phase 2 \quad Positioning \& Role Transition \hfill \normalfont\small 2027 -- 2029}
% ════════════════════════════════════════════════════════════════════════════

\bglabel{BG-03}{Transition into a Strategy-Adjacent Role at Collins}

\annualobjective{AO-02}{Secure a strategy-adjacent role or formal corporate strategy function within 
Collins at Senior Manager level or above.}{2027 -- 2028}

\initiative{IN-01}{Target and pursue corporate strategy role within Collins}
  {Strategy-adjacent role at Senior Manager level or above secured within Collins.}{2027 -- 2028}

\initiative{IN-02}{Develop financial modeling depth}
  {Financial modeling capability sufficient to contribute credibly to strategic analysis; 
  EMBA coursework and self-directed study applied.}{2027 -- 2029}

\gatecondition{2}{Strategy-adjacent role secured at Senior Manager level or above within Collins.}

\newpage

% ════════════════════════════════════════════════════════════════════════════
\section{Phase 3 \quad Visible Performance in Strategy Role\hfill \normalfont\small 2029 -- 2030}
% ════════════════════════════════════════════════════════════════════════════

Initiative detail for this phase is directional.
Full elaboration occurs at the Phase 2 annual review once Gate 2 is cleared.

\vspace{4pt}

\bglabel{BG-04}{Own at Least One Consequential Strategic Work Product Informing an Executive Decision}

\annualobjective{AO-01}{Deliver a strategic work product that directly informs a senior executive decision.}{defined at Gate 2}

\initiative{IN-01}{Deliver executive-level strategic work product}
  {At least one strategic deliverable completed where the output is traceable to a consequential executive decision.}{2029 -- 2030}

\gatecondition{3}{At least one consequential strategic work product with traceable executive
decision completed; M\&A adjacent exposure initiated.}

\newpage

% ════════════════════════════════════════════════════════════════════════════
\section{Phase 4 \quad Evolve Skillset \& Future Optionality \hfill \normalfont\small 2030 -- 2031}
% ════════════════════════════════════════════════════════════════════════════

Initiative detail for this phase is directional.
Full elaboration occurs at the Phase 3 annual review once Gate 3 is cleared.

\vspace{4pt}

\bglabel{BG-05}{Positioned Credibly for a Corporate Development Role with M\&A Exposure}

\annualobjective{AO-01}{Establish the credentials and positioning required to compete credibly for 
a corporate development role at a large A\&D prime.}{defined at Gate 3}

\initiative{IN-01}{M\&A adjacent exposure and financial modeling depth}
  {Meaningful M\&A adjacent experience accumulated; financial modeling depth sufficient to 
  compete as a serious candidate.}{2030 -- 2031}

\initiative{IN-02}{Assess CVC and external optionality}
  {Corporate venture capital and external market options assessed; positioning toward highest-value 
  path confirmed or revised.}{2030 -- 2031}

\gatecondition{4}{Credibly positioned for a corporate development role at a large A\&D prime;
CVC optionality assessed.}

\end{document}
